---
title: "Class 1: Basic R"
author: "Daniel Nicola"
#date: ' `r Sys.Date()`'
output: 
    html_notebook:
      toc: true
      toc_float: true
---

## R Basics
Let's have a look at the RStudio IDE. You can choose the best appearance according to your own taste. You can do this in Tools > Global Options > Appearance. 

*Recommended:* Configure Git (after having downloaded it)

## R Studio IDE
### The Console
You can run any code directly in the console. Just write it and press enter. Results are also shown in the console.

### The Workspace
Any values, functions, objects in general are loaded into the environment. Any object is added to the workspace and can be deleted with `rm()`. You can save and load workspaces.

### The Source
The source pane is the one where your scripts are shown. Depending on the file you're working with, the options in this pane change.

### R Chunks
We'll have a more detailed explanation when we check R Markdown out. Nevertheless, I'll be using it to generate html files with text and the codes we generate in class.

```{r}
2+2
```
## R Operations and Data Structures
### Basic Operations
- Addition
- Substraction
- Division
- Multiplication
- Exponentiation
- Modulo

```{r}
2+2
4-2
4/2
4*2
4^2
5%%2
```

### Variables
Assign a value to a variable with `<-`. All variables are then shown in the environment. Variables can be numeric, character, logical. To see which type of variable you are dealing with, you can use `class()`.
```{r}

```

### Vectors
```{r}

```

### Matrix
```{r}

```

### Data Frame

```{r}

```

### List


